Communication complexity: Chapter 3 \\ Distributional communication complexity

### 2019-01-25 CS860-CommunicationComplexity/assignments/Chapter3.tex
almost done

\begin{proof}
Let $\pi$ be the protocol attaining $D_\epsilon^{\mathrm{unif}}(f)$. Since $\Pr[\pi(x,y) \neq f(x,y)] \leq \epsilon$ and $\Pr[\pi(x,y) = f(x,y)] \geq 1-\epsilon$,
$$1-2\epsilon \leq \Pr[\pi(x,y) = f(x,y)] - \Pr[\pi(x,y) \neq f(x,y)].$$
Let $\{R_1, \dots, R_t\}$ be set of $f$-monochromatic rectangles corresponding to the path from the root of $\pi$ to each respective leaf. Then
$$\Pr[\pi(x,y) = f(x,y)] = \sum_{i=1}^t \Pr((x,y) \in R_i)\Pr(\pi(x,y) = f(x,y) \mid(x,y) \in R_i) = \sum_{i=1}^t \frac{|R_i|}{|\calX||\calY|}\frac{|R_i\cap f^{-1}(\pi(x,y))|}{|R_i|}.$$
Symmetrically
$$\Pr[\pi(x,y) \neq f(x,y)] = \frac{1}{|\calX||\calY|} \sum_{i=1}^t|R_i \cap f^{-1}(\pi(x,y)\oplus 1)|.$$
Thus we have
\begin{align*}1-2\epsilon &= \Pr[\pi(x,y) = f(x,y)] - \Pr[\pi(x,y) \neq f(x,y)] \\
&= \frac{1}{|\calX||\calY|} \sum_{i=1}^t|R_i\cap f^{-1}(\pi(x,y))| -|R_i \cap f^{-1}(\pi(x,y)\oplus 1)| \\
&\leq \frac{1}{|\calX||\calY|} \sum_{i=1}^t  \left| \sum_{(x,y) \in R_i} \big(M^{\pm}_f\big)_{x,y} \right|\\
&\leq t\cdot\discu(f).\end{align*}
Since $\log_2(t) = D_\epsilon^{\mathrm{unif}}(f)$ this completes the proof.
\end{proof}

@@

\begin{proof}
Let $\pi$ be the protocol attaining $D_\epsilon^{\mu}(f)$. Since $\Pr[\pi(x,y) \neq f(x,y)] \leq \epsilon$ and $\Pr[\pi(x,y) = f(x,y)] \geq 1-\epsilon$,
$$1-2\epsilon \leq \Pr[\pi(x,y) = f(x,y)] - \Pr[\pi(x,y) \neq f(x,y)].$$
Let $\{R_1, \dots, R_t\}$ be set of $f$-monochromatic rectangles corresponding to the path from the root of $\pi$ to each respective leaf. Then
$$\Pr[\pi(x,y) = f(x,y)] = \sum_{i=1}^t \Pr[(x,y) \in R_i \text{ and }\pi(x,y) = f(x,y) ] = \sum_{i=1}^t \mu(R_i \cap f^{-1}(\pi(x,y))).$$
Symmetrically
$$\Pr[\pi(x,y) \neq f(x,y)] = \sum_{i=1}^t\mu(R_i \cap f^{-1}(\pi(x,y)\oplus 1)).$$
Thus we have
\begin{align*}1-2\epsilon &= \Pr[\pi(x,y) = f(x,y)] - \Pr[\pi(x,y) \neq f(x,y)] \\
&=\sum_{i=1}^t|\mu(R_i\cap f^{-1}(\pi(x,y))) -\mu(R_i \cap f^{-1}(\pi(x,y)\oplus 1))| \\
&\leq \sum_{i=1}^t \disc_\mu(f)\\
&= t\cdot\disc_\mu(f).\end{align*}
Since $\log_2(t) = D_\epsilon^{\mu}(f)$ this completes the proof.
\end{proof}

@@

@@

>>>>

\begin{proof}
Let $\pi$ be the protocol attaining $D_\epsilon^{\mathrm{unif}}(f)$. Since $\Pr[\pi(x,y) \neq f(x,y)] \leq \epsilon$ and $\Pr[\pi(x,y) = f(x,y)] \geq 1-\epsilon$,
$$1-2\epsilon \leq \Pr[\pi(x,y) = f(x,y)] - \Pr[\pi(x,y) \neq f(x,y)].$$
Let $\{R_1, \dots, R_t\}$ be set of nearly $f$-monochromatic rectangles corresponding to the path from the root of $\pi$ to each respective leaf. Then
$$\Pr[\pi(x,y) = f(x,y)] = \sum_{i=1}^t \Pr((x,y) \in R_i)\Pr(\pi(x,y) = f(x,y) \mid(x,y) \in R_i) = \sum_{i=1}^t \frac{|R_i|}{|\calX||\calY|}\frac{|R_i\cap f^{-1}(\pi(x,y))|}{|R_i|}.$$
Symmetrically
$$\Pr[\pi(x,y) \neq f(x,y)] = \frac{1}{|\calX||\calY|} \sum_{i=1}^t|R_i \cap f^{-1}(\pi(x,y)\oplus 1)|.$$
Thus we have
\begin{align*}1-2\epsilon &= \Pr[\pi(x,y) = f(x,y)] - \Pr[\pi(x,y) \neq f(x,y)] \\
&= \frac{1}{|\calX||\calY|} \sum_{i=1}^t|R_i\cap f^{-1}(\pi(x,y))| -|R_i \cap f^{-1}(\pi(x,y)\oplus 1)| \\
&\leq \frac{1}{|\calX||\calY|} \sum_{i=1}^t  \left| \sum_{(x,y) \in R_i} \big(M^{\pm}_f\big)_{x,y} \right|\\
&\leq t\cdot\discu(f).\end{align*}
Since $\log_2(t) = D_\epsilon^{\mathrm{unif}}(f)$ this completes the proof.
\end{proof}

@@

\begin{proof}
Let $\pi$ be the protocol attaining $D_\epsilon^{\mu}(f)$. Since $\Pr[\pi(x,y) \neq f(x,y)] \leq \epsilon$ and $\Pr[\pi(x,y) = f(x,y)] \geq 1-\epsilon$,
$$1-2\epsilon \leq \Pr[\pi(x,y) = f(x,y)] - \Pr[\pi(x,y) \neq f(x,y)].$$
Let $\{R_1, \dots, R_t\}$ be set of nearly $f$-monochromatic rectangles corresponding to the path from the root of $\pi$ to each respective leaf. Then
$$\Pr[\pi(x,y) = f(x,y)] = \sum_{i=1}^t \Pr[(x,y) \in R_i \text{ and }\pi(x,y) = f(x,y) ] = \sum_{i=1}^t \mu(R_i \cap f^{-1}(\pi(x,y))).$$
Symmetrically
$$\Pr[\pi(x,y) \neq f(x,y)] = \sum_{i=1}^t\mu(R_i \cap f^{-1}(\pi(x,y)\oplus 1)).$$
Thus we have
\begin{align*}1-2\epsilon &= \Pr[\pi(x,y) = f(x,y)] - \Pr[\pi(x,y) \neq f(x,y)] \\
&=\sum_{i=1}^t|\mu(R_i\cap f^{-1}(\pi(x,y))) -\mu(R_i \cap f^{-1}(\pi(x,y)\oplus 1))| \\
&\leq \sum_{i=1}^t \disc_\mu(f)\\
&= t\cdot\disc_\mu(f).\end{align*}
Since $\log_2(t) = D_\epsilon^{\mu}(f)$ this completes the proof.
\end{proof}

@@

\begin{proof}
Let $\pi$ be the protocol attaining $D_\epsilon^{\mu}(f)$.
Let $\{R_1, \dots, R_t\}$ be set of nearly $f$-monochromatic rectangles corresponding to the path from the root of $\pi$ to each respective leaf.

$$1= \sum_{i=1}^t \mu(R_i) = \sum_{i=1}^t \mu(R_i \cap f^{-1}(0)) + \mu(R_i\cap f^{-1}(1)) \geq \alpha - t \beta +\mu(f^{-1}(1))$$
Thus
$$t \geq \frac{\alpha + \mu(f^{-1}(1)) -1}{\beta}.$$
Now we claim that 
$$\alpha + \mu(f^{-1}(1)) -1 \geq \alpha\cdot \mu(f^{-1}(1)) -\epsilon.$$
This claim is equivalent to
$$1-\epsilon \leq \alpha(\mu(f^{-1}(0))) +\mu(f^{-1}(1)).$$
This holds since $1-\epsilon$ is the probability of success \replacethistext{(I didn't have time to formalize)}.
\end{proof}

@@

\begin{proof}
From Proposition $1$, if $R = A\times B \subseteq 2^{[n]}\times 2^{[n]}$ is rectangle such that
$$\mu(R) \geq 2^{-\delta\sqrt{n}}$$ then
$$\mu(R\cap \Disj^{-1}(0)) > \alpha \mu(R).$$	
Thus any rectangle $R$ satisfies
$$\mu(R\cap \Disj^{-1}(0)) > \alpha \mu(R) - 2^{-\delta\sqrt{n}}.$$
So by the corruption bound with $\alpha$ and $\beta = 2^{-\delta\sqrt{n}}$ we obtain
$$D^{\mu}_\epsilon(\Disj) \geq \log(\frac{\alpha\cdot \mu(f^{-1}(1)) - \epsilon}{2^{-\delta\sqrt{n}}}) \geq \Omega(\sqrt{n}).$$\end{proof}
